The Asteroseismic Imprints of Mass Transfer

### 2024-04-08 paper/paper_AA.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/HRD_binary_compromise.pdf}
    \caption{Hertzsprung-Russell diagram showing the evolution of the binary. Tracks are coloured by the mass loss and mass accretion rate for the donor (marked D1-5) and accretor (marked A1-4), see Section~\ref{sec:hrd} for an explanation of the labels. We limit the accretion on the companion to $0.5 \, {\rm M_\odot}$ and follow its further evolution until core hydrogen exhaustion, see Section~\ref{sec:model_setup} for details on the technical implementation. We note the point at which $0.5 \, {\rm M_\odot}$ of material has been accreted by the accretor with a black plus sign. For reference, we show single star tracks as dashed light grey curves, with masses from $3$ to $4 \, {\rm M_\odot}$ in $0.1 \, {\rm M_\odot}$ intervals. Interactive plot available online \href{www.tomwagg.com/html/interact/mass-gainer-asteroseismology.html\#fig1}{\faChartArea}.}
    \label{fig:hrd}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/HRD_binary_compromise.pdf}
    \caption{Hertzsprung-Russell diagram showing the evolution of the binary. Tracks are coloured by the mass loss and mass accretion rate for the donor (marked D1-5) and accretor (marked A1-4), see Section~\ref{sec:hrd} for an explanation of the labels. We limit the accretion on the companion to $0.5 \, {\rm M_\odot}$ and follow its further evolution until core hydrogen exhaustion, see Section~\ref{sec:model_setup} for details on the technical implementation. \referee{The point at which $0.5 \, {\rm M_\odot}$ of material has been accreted is noted with a grey circle and subsequent evolution is highlighted in grey.} For reference, we show single star tracks as dashed light grey curves, with masses from $3$ to $4 \, {\rm M_\odot}$ in $0.1 \, {\rm M_\odot}$ intervals. Interactive plot available online \href{www.tomwagg.com/html/interact/mass-gainer-asteroseismology.html\#fig1}{\faChartArea}.}
    \label{fig:hrd}
\end{figure}
